Evaluate PEER in each cohort and brain region

### 2021-02-24 combined_analysis/eval_resid_in_each.Rmd
add more summary info

```{r ancestry}
fig1 = ggplot(ANCESTRY.MPP, aes(EV.1, EV.2, color=Cluster)) + geom_point() + ggtitle("MPP ancestry")  + theme(aspect.ratio=1)
fig2 = ggplot(ANCESTRY.HBCC, aes(EV.1, EV.2, color=as.character(cluster))) + geom_point() + ggtitle("HBCC ancestry")  + theme(aspect.ratio=1)
fig3 = ggplot(ANCESTRY.HBCC, aes(EV.1, EV.2, color=Population)) + geom_point() + ggtitle("HBCC ancestry") + theme(aspect.ratio=1)
plot_grid(fig1, fig2, fig3, nrow=1)
```

>>>>

```{r ancestry, fig.height=12}
ggplot(ANCESTRY.MPP, aes(EV.1, EV.2, color=Cluster)) + geom_point() + ggtitle("MPP ancestry")  + theme(aspect.ratio=1)
ggplot(ANCESTRY.HBCC, aes(EV.1, EV.2, color=as.character(cluster))) + geom_point() + ggtitle("HBCC ancestry")  + theme(aspect.ratio=1)
ggplot(ANCESTRY.HBCC, aes(EV.1, EV.2, color=Population)) + geom_point() + ggtitle("HBCC ancestry") + theme(aspect.ratio=1)
```
